ITP4887_AY2223_WrittenTestBeta_Student
Question B1
a.	Request the server to return an HTML document and store the result to the object html. The address of the server is given to the object url.
```{r}
require(rvest)
url <- "movie.html"
html <- read_html(url)
```

b.	Extract the content of table tag and store it into the object "node". (Hint: you can use the value from the previous answer)
```{r}
node <- html_elements(html,"table td")
node
```

c.	Convert the extracted value in node to Dataframe and store it into object budget. (Hint: you can use the value from the previous answer)
```{r}
node <- html_text(node)
budget <- data.frame(node)
budget
```

```{r}
budget <- data.frame(
  ReleaseDate = c("Apr 23, 2019", "Aug 26, 2020"),
  MovieName = c("Avengers: Endgame", "Tenet"),
  Budget = c("$400,000,000", "$205,000,000")
)
budget
```

d.	Assume that the data type of the release date is a string. Convert the release date to date type. (Hint: you can use the value from the previous answer)
```{r}
Sys.setlocale("LC_TIME", "English")
budget$ReleaseDate <- as.Date(budget$ReleaseDate,format = "%b %d, %Y")
budget
```

e.	Find all movies that were released in April 2022
(Hint: you can use the value from the previous answer)
```{r}
#budget[budget$ReleaseDate > "2022-04-01" & budget$ReleaseDate < "2022-05-01",]
budget[budget$ReleaseDate > "2019-04-01" & budget$ReleaseDate < "2019-05-01",]
```

Question B2
Write R code to
a.	import the dataset to the working environment and store it to the object student. Suppose the user will select the dataset file through the file directory.
```{r}
path <- file.choose()
student <- read.csv(path)
student
```

b.	extract each student's registration year from the studentID using the stringr package and add the data to the dataframe as a new column named registrationyear. Suppose the first two digits of studentID are the registration year.
```{r}
student$registrationyear <- substr(student$StudentID,1,2)
student
```

c.	amend the inappropriate ProgrammeCode with respect to the below reference table, named ref, using merge().
```{r}
ref <- data.frame(Wrong = c("DSANo.1","D SA","ES","Software","GDS","GG"),
                  Correst = c("DSA","DSA","SE","SE","GSD","GSD"))

ref
studentMerge <- merge(student,ref,by.x = "ProgrammeCode",by.y = "Wrong",all.x = T)
studentMerge
studentMerge$ProgrammeCode <- ifelse(is.na(studentMerge$Correst),studentMerge$ProgrammeCode,studentMerge$Correst)
studentMerge[,-ncol(studentMerge)]
```

Question B3
```{r}
Record <- data.frame(data = seq.Date(from = as.Date("2021-07-01"),to = as.Date("2021-07-10"),by = "day"),
                     temperature = c(32,33,28,30,33,33,31,33,29,29),
                     humidity = c(31,43,35,37,47,37,32,47,30,43),
                     WindSpeed = c(18,16,15,17,19,18,17,15,20,18))
Record
```

a.	calculate the water vapour pressure value and add it to the dataframe as a new column named WVP. This is the equation of water vapour pressure:
```{r}
Record$WVP <- Record$humidity / 100 * 6.105 * exp(17.27 * Record$temperature / (237.7 + Record$temperature))
Record
```

b.	calculate the apparent temperature value and add it to the dataframe as a new column named AT. This is the equation of apparent temperature.
```{r}
Record$AT <- 1.04 * Record$temperature + 0.2 * Record$WVP + 0.65 * Record$WindSpeed - 2.7
Record
```

c. calculate the average apparent temperature by weekday.
```{r}
weekday <- weekdays(Record$data)
Avgtemp <- tapply(Record$AT,weekday,mean)
Avgtemp
```

d. delete the columns humidity and WVP.
```{r}
Record$humidity <- NULL
Record$WVP <- NULL
Record
```

