AY2122_4887_Test
Question B1
```{r}
BodyMass <- data.frame(Name = c("Markayla Lanier","Mufeed al-Ameen","Vanessa Louailler",
                                "Quy Canono","Shaakira el-lqbal","Madeleine Martinez",
                                "Edward Roland","Glenda Caranza","Jeremiah Abachiche","Audrey Flores"),
                       Gender = c("Male","Female","Male","Male","Female","Female","Male",
                                  "Female","Female","Male"),
                       Height = c(176,171,164,177,164,177,177,170,170,151),
                       Weigth = c(69,66,66,46,79,72,68,51,50,60))
BodyMass
```

a.	Update the Name "Vanessa Louailler" to "Benson Lau".
```{r}
BodyMass$Name[BodyMass$Name == "Vanessa Louailler"] <- "Benson Lau"
BodyMass
```

b.	find all the Male that their Height is taller than 170.
The result only includes the column "Name" and "Height".
```{r}
result <- BodyMass[BodyMass$Gender == "Male" & BodyMass$Height > 170,c("Name","Height")]
result
```

c.Delete the column Gender.
```{r}
BodyMass$Gender <- NULL
BodyMass
```

d.	Suppose the unit of the Height and the Weight is centimetre and kilogramme, respectively. Then, add a new column "BMI" to the "BodyMass", and the value should base on the below formula:
BMI = Weight in kilogrammme / (Height in metre)^2
```{r}
BodyMass$BMI <- BodyMass$Weigth / (BodyMass$Height / 100)^2
BodyMass
```

Question B2
```{r}
BookSale <- data.frame(bookName = c("Tensei Shitara Suraimu datta Ken",
                                    "Miss Kobayashi's Dragon Maid",
                                    "Y<U+014D>jo Senki",
                                    "Pokemon",
                                    "RWBY"),
                       SaleVolume = c(5000,15353,5432,33455,1594433),
                       PublishRegion = c("Japan","Japan","Japan","Japan","Europe"))

BookInformation <- data.frame(bookName = c("Tensei Shitara Suraimu datta Ken",
                                           "Miss Kobayashi's Dragon Maid",
                                           "Y<U+014D>jo Senki",
                                           "Pokemon",
                                           "RWBY"),
                              price = c("5531JPY","3775JPY","2600JPY","10000JPY","160EUR"))
BookSale
BookInformation
```

a.	combine the above datasets to a single dataframe object Bookstat by sqldf(). Assume the sqldf package is imported. And, below is the sample for reference.
```{r}
require("sqldf")
Bookstat <- sqldf("select S.bookName, SaleVolume,PublishRegion,price
                  from BookSale S, BookInformation I
                  where S.bookName = I.bookName;")
Bookstat
```

b.	Exchange all the currency of the price to HKD. The following is the exchange rate:
i.	JPY : HKD = 1: 0.070755877
ii.	EUR : HKD = 1 : 9.1951366
```{r}
require(stringr)
Bookstat$priceValue <- as.numeric(str_extract(Bookstat$price,"\\d+"))
Bookstat$priceUnit <- str_extract(Bookstat$price,"[a-zA-Z]+")
Bookstat$priceValue <- unlist(mapply(function(x,y){
  if(y == "JPY"){
    x <- x * 0.070755877
  }else if(y == "EUR"){
    x <- x *9.1951366
  }else{
    x <- x
  }
},  Bookstat$priceValue,
  Bookstat$priceUnit
))
Bookstat$priceUnit <- "HKD"
Bookstat$priceHKD <- paste0(as.integer(Bookstat$priceValue), Bookstat$priceUnit)
Bookstat[,c("bookName","SaleVolume","PublishRegion","price","priceHKD")]
```

c.	calculate the revenue by Publishregion by tapply(). (hint: Revenue = SaleVolume x price)
```{r}
revenue <- Bookstat$SaleVolume * Bookstat$priceValue
regionrevenue <- data.frame(tapply(revenue,Bookstat$PublishRegion,sum))
regionrevenue
```

Question B3
a.	read the HTML document from the webpage "http://IT114116.edu.hk" and store the result to the object html.
```{r}
require("rvest")
#html <- read_html("http://IT114116.edu.hk")
html <- read_html("https://poe.com/")
```

b.	Extract elements from all anchor tags and store into the object "node".
(Hint: you can use the value from previous answer)
```{r}
node <- html_elements(html,"a")
node
```

c.	extract the URL link from the anchor tag and store it in full URL format into the object URL.
Full URL example: "http://IT114116.edu.hk/notice/12378.html" (Hint: you can use the value from previous answer)
```{r}
URL <- html_attr(node,"href")
URL
```

Question B4
```{r}

```
